Highlighting Disputed Claims on the Web

### 2009-10-29 papers/www_disputefinder/disputefinder.tex
Folded in JM's changes

The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}. If a user is to gain a broad understanding of a topic then they will need to either spend time looking for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information. Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.

@@

Dispute Finder consists of a database, an API, and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_claim_article}). The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claim. The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims. The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.

@@

\begin{description}
\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large and credible. If the database is too small then users will rarely see snippets highlighted. If a snippet is highlighted but there is no credible evidence for other points of view, then users will find Dispute Finder annoying. We currently crowd-source claims from users, and mine disputed claims from web sites such as Snopes and Politifact that already maintain lists of disputed claims.

@@

According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust. Their 2008 survey found that 33\% of registered democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says. Pew also found that online sources are viewed with more skepticism than their print, broadcast, and cable counterparts.

@@

Fact checking web sites and search engines work great when you know something is disputed, but are of little use if you did not realize that what you were reading was disputed. The primary aim of Dispute Finder is to let you know when something you are reading is disputed.

@@

This database should not contain contain everything that has ever been disputed by anyone. In some sense almost everything is disputed by someone on the web. There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless. Similarly, there is little point spending effort rebutting claims that nobody believes. For example there is reliable evidence that the moon is made of cheese, but few people believe this claim is true. What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.

@@

Currently most of our claims are automatically mined Snopes and Politifact. Both of these sites maintain well curated databases of disputed claims, together with information about them. Snopes has good coverage of urban myths, and Politifact has good coverage of claims made by American Policitians. In the future we plan to crawl other sites that cover other kinds of disputed claims (e.g. medical claims) and to provide an API to allow any site to provide a well-structured feed that we can use. At the time of writing, Dispute Finder has imported 1,457 claims from Snopes and 595 claims from Politifact.

We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}). The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org. It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim. When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing article.

The automatic import feeds allow Dispute Finder to bootstrap a large database of disputed claims without needing a large active user community and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.

@@

Given a web page, Dispute Finder needs to identify which snippets are making known disputed claims. Our current implementation runs a simple textual entailment algorithm inside the browser to look for sentences that entail known disputed claims.

@@

\item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier. We used a simple baysian classifier with n-grams as features. This classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.  Once the classifier has been trained, the server uses it to automatically choose which of the rest of the results from Yahoo BOSS should be marked (Figure~\ref{training}).

@@

Explicit page marking has the highest accuracy, but the poorest coverage. Since a user is looking at the page in its entirety, they can read the snippet in context and make a good judgment about whether the snippet is indeed making the claim. However the manual effort required per page makes it difficult for this approach to scale. We also found that it can also be hard to motivate a user to mark snippets if they think that it is unlikely that another user with the Dispute Finder extension will read exactly this page. This same problem that has hindered the adoption of numerous web page annotation tools.

Bulk page marking trades off some accuracy for better coverage. When a user searches for a phrase, they can quickly find hundreds of snippets and mark them by clicking on them. Since they are reading the snippet out of context, they are more likely to mark a phrase incorrectly.

Server side classification trades off more accuracy for more coverage. The classifier can mark more pages than a user could ever mark manually, and can keep marking new pages as they appear, but it is inevitably less accurate than a human.

Client side entailment gets the most coverage. Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined. This is particularly important for news pages, which are frequently read only a few minutes after they have been written. Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and information on an intranet.

@@

The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}. Our implementation divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist. Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}. Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions. Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.

@@

The authors of MemeTracker observed that many ideas often flow around the web in the form of ``memes'' that are repeated on many web sites with relatively little variation. MemeTracker uses this to track the way an idea propagates across the web using a relatively simple algorithm. We have found that the precision and recall of our client-side textual entailment algorithm varies hugely depending on how meme-like a claim is. Some claims (particularly those derived from quotes) are widely repeated almost-verbatim, and can be detected relatively easily. However many other claims are rarely stated explicitly in a single sentence or with the same choice of words, making them much harder to detect with a simple algorithm.

@@

When a user clicks on a highlighted snippet, Dispute Finder displays a popup interface with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read. In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}). We also implemented and tested an interface that contained a user-editable argumentation graph, however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.

If a user clicks on a highlighted snippet, Dispute Finder will bring up a popup interface explaining the different alternative points of view. We could have omitted this feature and still had a useful system. Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim. There are however several reasons why it makes sense for Dispute Finder to maintain information about a disputed claim:

@@

Unfortunately, as Pew report~\cite{PewResearch2008}, while most people say they want to receive information ``without a point of view'', the sites people actually trust tend to be those that share the person's own point of view. It seems that ``without a point of view'' is a similar concept to ``without an accent''. As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa. Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments. Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.

>>>>

The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}. If a user is to gain a broad understanding of a topic then they will need to either spend time searching for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information. Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.

@@

Dispute Finder consists of a server-side database, an API, and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_claim_article}). The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claim. The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims. The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.

@@

\begin{description}
\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large and credible. If the database's coverage is too small then users will rarely see snippets highlighted. If a snippet is highlighted but there is no credible evidence for other points of view, then users will find Dispute Finder annoying. We currently crowd-source claims from users, and mine disputed claims from web sites such as Snopes and Politifact that already maintain lists of disputed claims.

@@

According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust. Their 2008 survey found that 33\% of registered Democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says. Pew also found that online sources are viewed with more skepticism than their print, broadcast, and cable counterparts.

@@

Fact checking web sites and search engines work well when you know something is disputed, but are of little use if you did not realize that what you were reading was disputed. The primary aim of Dispute Finder is to let you know when something you are reading is disputed.

@@

This database should not contain contain everything that has ever been disputed by anyone. In some sense almost everything is disputed by someone on the web. There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless. Similarly, there is little point spending effort rebutting claims that nobody believes. For example there is reliable evidence opposing the claim that the moon is made of cheese, but few people believe this claim is true. What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.

@@

Currently most of our claims are automatically mined from Snopes and Politifact. Both of these sites maintain well curated databases of disputed claims, together with information about them. Snopes has good coverage of urban myths, and Politifact has good coverage of claims made by American Policitians. In the future we plan to crawl other sites that cover other kinds of disputed claims (e.g. medical claims) and to provide an API to allow any site to provide a well-structured feed that we can use. At the time of writing, Dispute Finder has imported 1,457 claims from Snopes and 595 claims from Politifact.

We also provide users means to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}). The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org. It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim. When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing article.

The automatic import bootstraps Dispute Finder with a large database of disputed claims without needing a large active user community, and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.

@@

To highlight disputed snippets on a web page, Dispute Finder needs to identify which snippets are making known disputed claims. Our current implementation runs a simple textual entailment algorithm inside the browser to look for sentences that entail known disputed claims.

@@

\item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier. We used a simple Baysian classifier with n-grams as features. This classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.  Once the classifier has been trained, the server uses it to refine which of the rest of the results from Yahoo BOSS should be marked (Figure~\ref{training}).

@@

Explicit page marking has the highest precision, but the poorest coverage. Since a user is looking at the page in its entirety, they can read the snippet in context and make a good judgment about whether the snippet is indeed making the claim. However the manual effort required per page makes it difficult for this approach to scale. We also found that it can also be hard to motivate a user to mark snippets if they think that it is unlikely that another user with the Dispute Finder extension will read exactly this page. This same problem that has hindered the adoption of numerous web page annotation tools.

Bulk page marking trades off some precesion for better coverage. When a user searches for a phrase, they can quickly find hundreds of snippets and mark them by clicking on them. Since they are reading the snippet out of context, they are more likely to mark a phrase incorrectly.

Server side classification trades off more precision for more coverage. The classifier can mark more pages than a user could ever mark manually, and can keep marking new pages as they appear, but it is inevitably less accurate than a human.

Client side entailment gets the most coverage. Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined. This is particularly important for news pages, which are frequently read only a few minutes after they are posted. Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and information on an intranet.

@@

Detecting entailment between texts is a semantic analyss problem. Our client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}. Our implementation divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist. Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using Baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}. Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions. Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.

@@

The authors of MemeTracker observed that many ideas often flow around the web in the form of ``memes'' that are repeated on many web sites with relatively little variation. To the extent that this is true, it simplifies identifying snippets that repeat the idea. MemeTracker uses this to track the way an idea propagates across the web using a relatively simple algorithm. We have found that the precision and recall of our client-side textual entailment algorithm varies hugely depending on how meme-like a claim is. Some claims (particularly those derived from quotes) are widely repeated almost-verbatim, and can be detected relatively easily. However many other claims are rarely stated explicitly in a single sentence or with the same choice of words, making them much harder to detect with a simple algorithm.

@@

When a user clicks on a highlighted snippet, Dispute Finder displays a popup pane with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read. In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}). We also implemented and tested an interface that contained a user-editable argumentation graph, however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.

We could have omitted this claim-information feature and still had a useful system. Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim. There are however several reasons why it makes sense for Dispute Finder to maintain information about a disputed claim:

@@

Unfortunately, as Pew Research discovered~\cite{PewResearch2008}, while most people say they want to receive information ``without a point of view'', the sites people actually trust are often those that share the person's own point of view. It seems that ``without a point of view'' is a similar concept to ``without an accent''. Similarly, Manjou~\cite{Manjou2008} found that people tend to measure the reliablity of a source based on how well it fits with what they already believe to be true.  As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa. Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments. Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.
